Visualizations for the manuscript

### 2022-04-04 metanalysis_visualization/manuscript_Figures.Rmd
sex difference bootstrap

bootstrapped_fitted_all <-  bootstrapped_fitted_all %>%
  filter( time_p <= end_date_plots &
          time_p >= start_date_plots)

count_icd_all <-  count_icd_all %>%
  filter( time_p <= end_date_plots &
          time_p >= start_date_plots)

patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>%
  filter( time_p <= end_date_plots &
          time_p >= start_date_plots)

patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc_all %>%
  filter( time_p <= end_date_plots &
          time_p >= start_date_plots)

perc_disorder_group_all <- perc_disorder_group_all %>%
  filter( time_p <= end_date_plots &
          time_p >= start_date_plots)

ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy_all %>%  
  filter( time_p <= end_date_plots &
          time_p >= start_date_plots)
```

@@

```{r}
annotation_function <- function(df, ...) {
  z <- unique(df[["observed_diff"]]) / sd(df[["periodduring_pandemic:time"]])
  pvalue_coeff_interaction = round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  paste0("Coeffs differences: ",
         round(unique(df[["observed_diff"]]), 2),
         " (pvalue: ",
         pvalue_coeff_interaction,
         ")")
}
```

@@

```{r}
df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid")

df_coefficients_boot <- df_coefficients_boot %>%
  left_join( country_map )

@@

```{r}
### January 19-May 21
bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  left_join( country_map )

quantile_bootstrapped_fitted_all <- quantile_bootstrapped_fitted_all %>%
  left_join( country_map )

count_icd_all_boot <- count_icd_all_boot %>%
  left_join( country_map )

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = count_icd_all_boot,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all_extended.png", height = 20, width = 32, units = "cm")
```

```{r}
patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>%
  left_join( country_map )

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

@@

```{r}
trends_country <- trends_siteid %>% 
  left_join(country_map, by = "plotsLabel") %>% 
  group_by(country) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

@@

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```

@@

```{r}
sexInfo_per_country <- table1_all %>%
  filter( Category == "Sex") %>%
  mutate ( counts_before = as.numeric(sapply(strsplit( as.character(before_pandemic), " "), '[', 1)), 
           counts_during = as.numeric(sapply(strsplit( as.character(during_pandemic), " "), '[', 1))) %>%
  select( name, siteid, counts_before, counts_during ) %>%
  inner_join( country_map ) %>%
  group_by( name, country ) %>%
  summarise( before = sum( counts_before), 
             during = sum( counts_during )) %>%
  pivot_longer(names_to = "period", cols=c(before, during))

sexInfo_all <- table1_all %>%
  filter( Category == "Sex") %>%
  mutate ( counts_before = as.numeric(sapply(strsplit( as.character(before_pandemic), " "), '[', 1)), 
           counts_during = as.numeric(sapply(strsplit( as.character(during_pandemic), " "), '[', 1))) %>%
  select( name, siteid, counts_before, counts_during ) %>%
  inner_join( country_map ) %>%
  group_by( name ) %>%
  summarise( before = sum( counts_before), 
             during = sum( counts_during )) %>%
  pivot_longer(names_to = "period", cols=c(before, during)) %>%
  mutate( country = 'ALL' ) %>%
  select( name, country, period, value ) %>%
  rbind( sexInfo_per_country)

sexInfo_all %>%
  ggplot( aes( x= name, y = value, fill = period )) +
  geom_bar( stat = "identity", position = "dodge") +
  facet_wrap("country", scales = "free_y") + 
  labs(x ="", y = "number of patients") +
  theme(axis.text.x=element_text(hjust=1, size = 8), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))+ 
  scale_fill_manual("Pandemic \n period", values = c("before" = "grey", "during" = "orange"))

@@

```{r}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_perc_all %>%
  select( - percentage ) %>%
  group_by( time_p, sex ) %>%
  mutate( total_cases = sum( count ), 
          sex_cases = sum( count_sex ), 
          percentage = 100* sex_cases / total_cases, 
          country = "ALL")

@@

```{r Interrupted time series by sex}
bootstrap_size = 10

patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc_all %>% 
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, period, sex, count, percentage, siteid)

bootstrapped_sex <- patients_hospitalized_agg_sex_perc_all %>%
  group_by(siteid, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map( ~bootstrapping_slopes(.x, group_name = .y, bootstrap_size = bootstrap_size, count = "count"))

@@

```{r Interrupted time series by sex}
quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  group_by(time_p, period, siteid, sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
```

```{r}
coefficients_df_sex <- patients_hospitalized_agg_sex_perc_all %>% 
  group_by(siteid, sex) %>% 
    mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

@@

```{r}
df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  left_join(coefficients_df_sex, by = c("siteid", "sex"))
```

```{r}
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
```

```{r}
# expand.grid(
#   unique(df_coefficients_boot_sex$siteid),
#   unique(df_coefficients_boot_sex$sex)
# ) %>% 
#   t() %>% 
#   paste(unique(.$siteid),
#         unique(.$sex), 
#         collapse = " "
#   )
# 
# names_plot_annotations_sex <- c()
# for (site in unique(df_coefficients_boot_sex$siteid)) {
#   for (sex in unique(df_coefficients_boot_sex$sex)) {
#     names_plot_annotations_sex <- c(names_plot_annotations_sex, paste(site, sex))
#   }
# }

# plot_annotations_sex <- df_coefficients_boot_sex %>% 
#   group_by(siteid, sex) %>% 
#   group_map( annotation_function ) %>% 
#   set_names(names_site_id) %>% 
#   unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  # label = plot_annotations
)
```

### Disorder group 
```{r}
perc_disorder_group_total <- perc_disorder_group_all %>%
  select( - percentage_dg ) %>%
  group_by( time_p, disorder_group ) %>%
  mutate( total_cases = sum( count_icd ), 
          dg_cases = sum( count_dg ), 
          percentage = 100* dg_cases / total_cases, 
          country = "ALL")

perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

@@

numberOfCodesPerDisorderGroup %>%
  mutate( disorder_group = swr( disorder_group ) ) %>%
  inner_join( country_map ) %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
```

@@

#### At site level
```{r}
library(reshape2)
count_icd_all <- count_icd_all %>%
  left_join( country_map )

>>>>

filter_by_dates <- function(df_,
                            start_date_plot,
                            end_date_plots) {
  df_[df_[["time_p"]] <= end_date_plots & df_[["time_p"]] >= start_date_plots, ]
}

bootstrapped_fitted_all <- filter_by_dates(bootstrapped_fitted_all, start_date_plots, end_date_plots)
count_icd_all <- filter_by_dates(count_icd_all, start_date_plots, end_date_plots)
patient_count_psy_period_psy_all <- filter_by_dates(patient_count_psy_period_psy_all, start_date_plots, end_date_plots)
patients_hospitalized_agg_sex_perc_all <- filter_by_dates(patients_hospitalized_agg_sex_perc_all, start_date_plots, end_date_plots)
perc_disorder_group_all <- filter_by_dates(perc_disorder_group_all, start_date_plots, end_date_plots)
ratios_patients_with_without_psy_all <- filter_by_dates(ratios_patients_with_without_psy_all, start_date_plots, end_date_plots)
```

# Add site complete name information

```{r}
bootstrapped_fitted_all <- left_join(bootstrapped_fitted_all, country_map, on = "site_id")
count_icd_all <- left_join(count_icd_all, country_map, on = "site_id")
patient_count_psy_period_psy_all <- left_join(patient_count_psy_period_psy_all, country_map, on = "site_id")
patients_hospitalized_agg_sex_perc_all <- left_join(patients_hospitalized_agg_sex_perc_all, country_map, on = "site_id")
perc_disorder_group_all <- left_join(perc_disorder_group_all, country_map, on = "site_id")
ratios_patients_with_without_psy_all <- left_join(ratios_patients_with_without_psy_all, country_map, on = "site_id")

@@

```{r}
annotation_function <- function(df, ...) {
  z <- unique(df[["observed_diff"]]) / sd(df[["periodduring_pandemic:time"]])
  pvalue_coeff_interaction <- round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  paste0("Coeffs differences: ",
         round(unique(df[["observed_diff"]]), 2),
         " (pvalue: ",
         format.pval(pvalue_coeff_interaction),
         ")")
}
```

@@

```{r}
df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid") %>% 
  left_join(country_map, by = "siteid")

@@

```{r}
bootstrapped_fitted_all <- bootstrapped_fitted_all %>% left_join(country_map, by = "siteid")

quantile_bootstrapped_fitted_all <- quantile_bootstrapped_fitted_all %>% left_join(country_map, by = "siteid")
```

```{r}
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

@@

```{r}
trends_country <- trends_siteid %>% 
  group_by(plotsLabel) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

@@

forest(model_meta_country, 
       slab = trends_country$plotsLabel,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```

@@

```{r}
sexInfo_per_country <- table1_all %>%
  filter( Category == "Sex") %>%
  mutate ( counts_before = as.numeric(sapply(strsplit( as.character(before_pandemic), " "), '[', 1)), 
           counts_during = as.numeric(sapply(strsplit( as.character(during_pandemic), " "), '[', 1))) %>%
  select( name, siteid, counts_before, counts_during ) %>%
  inner_join( country_map ) %>%
  group_by( name, country ) %>%
  summarise( before = sum( counts_before), 
             during = sum( counts_during )) %>%
  pivot_longer(names_to = "period", cols=c(before, during)) 
sexInfo_all <- table1_all %>%
  filter( Category == "Sex") %>%
  mutate ( counts_before = as.numeric(sapply(strsplit( as.character(before_pandemic), " "), '[', 1)), 
           counts_during = as.numeric(sapply(strsplit( as.character(during_pandemic), " "), '[', 1))) %>%
  select( name, siteid, counts_before, counts_during ) %>%
  inner_join( country_map ) %>%
  group_by( name ) %>%
  summarise( before = sum( counts_before), 
             during = sum( counts_during )) %>%
  pivot_longer(names_to = "period", cols=c(before, during)) %>%
  mutate( country = 'ALL' ) %>%
  select( name, country, period, value ) %>%
  rbind( sexInfo_per_country)
sexInfo_all %>%
  ggplot( aes( x= name, y = value, fill = period )) +
  geom_bar( stat = "identity", position = "dodge") +
  facet_wrap("country", scales = "free_y") + 
  labs(x ="", y = "number of patients") +
  theme(axis.text.x=element_text(hjust=1, size = 8), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))+ 
  scale_fill_manual("Pandemic \n period", values = c("before" = "grey", "during" = "orange"))

@@

```{r}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_perc_all %>%
  select( - percentage ) %>%
  group_by( time_p, sex ) %>%
  summarise( total = sum( count ), 
             count_sex = sum( count_sex ), 
             percentage = 100* count_sex / total, 
             siteid = "ALL")

@@

```{r Interrupted time series by sex}

patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_total %>% 
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, period, sex, count_sex, percentage, siteid)
# %>% 
#   inner_join(country_map)

bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "count_sex", 
                                  percentage = "percentage"))

@@

```{r Interrupted time series by sex}
quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
```

```{r}
coefficients_df_sex <- patients_hospitalized_agg_sex_total %>% 
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
    mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

@@

```{r}
df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  # left_join(coefficients_df_sex, by = c("plotsLabel", "sex"))
  left_join(coefficients_df_sex, by = c("sex"))
```

```{r}
names_sex <- unique(df_coefficients_boot_sex$sex)

## Using only male, but female and male necessarily yield equal p-values
plot_annotations_sex_df <- annotation_function(
  df_coefficients_boot_sex[df_coefficients_boot_sex$sex == "female", ]
) %>% data.frame(label = ., 
                 plotsLabel = "Female")

# plot_annotations_sex_df <- df_coefficients_boot_sex %>% 
#   group_by(sex) %>% 
#   group_map(annotation_function) %>%
#   paste(str_to_title(names_sex), ., sep = ": ") %>% 
#   as_tibble() %>% 
#   rename(label = value)
# bind_cols(group_names) %>% 
#                rename(label = value) %>% 
#                mutate(label = paste(stringr::str_to_title(sex), label, sep = ": ")) %>% 
#                mutate(plotsLabel = names_site_id)
#              , .keep = TRUE) %>% 
  # group_map( function(df, group_names) group_by(df, plotsLabel) %>%
  #              annotation_function() %>%
               # as_tibble() %>%
               # bind_cols(group_names) %>%
               # rename(label = value) %>%
               # mutate(label = paste(stringr::str_to_title(sex), label, sep = ": ")) %>%
  #              mutate(plotsLabel = names_site_id)
  #            , .keep = TRUE) %>% 
  # set_names(unique(df_coefficients_boot_sex$sex))

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  # geom_label(data = plot_annotations_sex_df[["male"]],
  #            aes(label=label),
  #            x = -Inf,
  #            y = 15,
  #            hjust = 0,
  #            vjust = 0,
  #            size = 4,
  #           inherit.aes = FALSE) +
  # ylim(10, 90) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
```
### Disorder group fix

```{r}

perc_disorder_group_total_fix <- perc_disorder_group_all %>%
  group_by( time_p, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             percentage = mean(percentage_dg * count_icd / total_diagnoses, na.rm = TRUE), 
             country = "ALL")

### Disorder group 
```{r}
perc_disorder_group_total_first <- perc_disorder_group_all %>%
  select( - percentage_dg ) %>%
  group_by( time_p, disorder_group ) %>%
  mutate( total_cases = sum( count_icd ), 
          dg_cases = sum( count_dg ), 
          percentage = 100* dg_cases / total_cases, 
          country = "ALL")

perc_disorder_group_total_fix %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

@@

numberOfCodesPerDisorderGroup %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
```

@@

#### At site level
```{r}
library(reshape2)
